\documentclass[10pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm,mathtools}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{microtype}
\usepackage[hidelinks]{hyperref}
\usepackage[nameinlink,noabbrev]{cleveref}

\newtheorem{definition}{Definition}
\newtheorem{conjecture}{Conjecture}
\newtheorem{obligation}{Proof Obligation}
\theoremstyle{definition}
\newtheorem{codesanity}{Code Sanity Check}
\newtheorem{remark}{Remark}

\newcommand{\TopK}{\operatorname{TopK}}
\newcommand{\polylog}{\operatorname{polylog}}
\newcommand{\Adv}{\operatorname{Adv}^{\pm}}
\newcommand{\cB}{\mathcal{B}}
\newcommand{\cM}{\mathcal{M}}
\newcommand{\cS}{\mathcal{S}}
\newcommand{\cT}{\mathcal{T}}
\newcommand{\eps}{\varepsilon}
\newcommand{\ket}[1]{\lvert #1\rangle}
\newcommand{\bra}[1]{\langle #1\rvert}
\newcommand{\status}[1]{\textsc{#1}}

\title{Q-GapSelect: An Audited Research Program for\\
Heterogeneous-Gap Quantum Top-$k$ Identification}
\author{Anonymous Authors}
\date{Research manuscript --- \today}

\begin{document}
\maketitle

\begin{center}
\fbox{\parbox{0.94\linewidth}{
\textbf{Claim-status notice.}
This manuscript specifies a research program; it does not report a proved
quantum advantage.  Q-GapSelect is \status{proposed}.  Its angular-gap upper
bound is a \status{conjecture}; sampler transport and direct-sum lower bounds are
\status{proof obligations}.  Finite code checks are not mathematical proofs.
The rejected mean-gap and fixed-smaller-side candidates are archived rather than
silently renamed.  No LLM quantum-query advantage is claimed.
}}
\end{center}

\begin{abstract}
Recent quantum algorithms already cover approximate $k$-minimum finding,
multiple-marked-element extraction, variable-time search, order statistics, and
single-output fixed-confidence best-arm identification.  Consequently, noisy
boundary localization, batch extraction, and the equal-gap Top-$k$ regime are not
by themselves new quantum contributions.  We isolate a narrower open candidate:
a tight fixed-confidence theorem for stochastic Top-$k$ identification with
unknown heterogeneous gaps, measured in the amplitude angle rather than raw mean
difference.  We distinguish a clean canonical block-rotation oracle from a
natural purification sampler with generator garbage; the latter is the relevant
interface for a reversible code-LLM surrogate and cannot be compressed to the
former for free.  We also replace a falsified fixed-cardinality output orientation
by a candidate minimum over selected-set and rejected-set certificates, approached
by dovetailing two independently verifiable procedures.  We state the proposed
Q-GapSelect architecture, its strongest black-box baselines, the precise
purification-transport and direct-sum obligations, and a deferred matroid
extension.  The accompanying implementation is an analytic canonical-oracle
sanity harness only.  Neither the heterogeneous upper bound, a matching quantum
lower bound, nor an LLM attack improvement has yet been established.
\end{abstract}

\section{Introduction}

Quantum best-arm identification (BAI) gives a gap-dependent fixed-confidence
speedup for one returned index~\cite{wang2021quantum}.  Multi-output selection is
subtler, but much of the apparent algorithmic machinery is already known.
Minimum and $k$-minimum search have a long history
~\cite{durr1996minimum,durr2006graph,miyamoto2019kminima}; Gao, Ji, and Wang
recently gave an almost optimal approximate $k$-minimum algorithm that explicitly
handles approximate value access and applies it to selecting expectation values
~\cite{gao2025approxkmin}.  Finding all marked elements with
$O(\sqrt{Nk})$ queries and polylogarithmic gate overhead is also known
~\cite{vanapeldoorn2024marked}.  Variable-time search
~\cite{ambainis2023variable}, order-statistic lower bounds
~\cite{nayak1999median}, and a time-efficient $k$-minimum data structure without
QRAM~\cite{wang2026rmq} further narrow the available novelty.

The viable question is therefore not whether amplitude estimation can be placed
inside Top-$k$.  It is whether one can prove a \emph{strictly stronger}
heterogeneous, fixed-confidence theorem than every black-box composition of those
results, under an honest stochastic sampler interface, and match it with an
all-algorithms lower bound.

Our audited candidate is Q-GapSelect.  Relative to the earlier draft, three
changes are fundamental.
\begin{enumerate}[leftmargin=*]
  \item We separate the exact clean block rotation used for synthetic analysis
  from a natural purification sampler that retains generator randomness and
  output garbage.
  \item We measure local statistical difficulty by the amplitude-angle gap
  $\gamma$, whose inverse is the correct local coherent-discrimination scale;
  raw mean gaps $\Delta$ are retained only for reporting and an interior
  corollary.
  \item We reject the rule \emph{enumerate the smaller cardinality side}.  Gap
  heterogeneity can make that side asymptotically more expensive.  The new
  candidate minimizes over two certificate orientations and proposes a
  first-verified-certificate dovetail.
\end{enumerate}

\paragraph{Current status.}
The oracle specifications and falsification criteria are complete.  The
orientation-aware complexity is a candidate functional.  The algorithm,
canonical upper bound, transfer to natural purification access, direct-sum lower
bound, and matroid extension remain unproved.  The current code estimates active
arms independently with an analytic canonical backend; it does not implement the
claimed coherent batch algorithm.

\section{Prior Work and the Remaining Novelty Boundary}

\paragraph{Estimation and single-output exploration.}
Amplitude estimation and source-code mean estimation are established
~\cite{brassard2002amplitude,kothari2023mean}; multivariate mean estimation also
has near-optimal algorithms in explicitly distinguished input models
~\cite{cornelissen2022multivariate}.  Quantum BAI already combines heterogeneous
gaps and variable-time ideas for one answer~\cite{wang2021quantum}.  Calling a
mean estimator inside elimination is thus a baseline, not a contribution.

\paragraph{Order statistics, approximate values, and batch output.}
D{\"u}rr--H{\o}yer minimum finding and later $k$-minimum procedures cover exact
values~\cite{durr1996minimum,miyamoto2019kminima}.  More importantly,
Gao--Ji--Wang cover approximate $k$-minimum finding for every $k$ and include
expectation-value applications~\cite{gao2025approxkmin}.  Nayak--Wu establish
quantum query bounds for medians and related statistics
~\cite{nayak1999median}.  Van Apeldoorn--Gribling--Nieuwboer give an optimal-query,
gate-efficient routine for all marked elements~\cite{vanapeldoorn2024marked}.
Therefore \textsc{QBoundary}, approximate comparisons, equal-gap selection, and
\textsc{QBatchExtract} cannot be advertised as new primitives.

\paragraph{Variable costs and output information.}
Ambainis--Kokainis--Vihrovs give improved upper and lower bounds for variable-time
quantum search~\cite{ambainis2023variable}.  Oracle interrogation shows that
returning a large structured answer can retain linear query cost
~\cite{vandam1998interrogation}, while strong direct-product methods constrain
query sharing across independent outputs~\cite{lee2012directproduct}.  These are
the required comparison tools for heterogeneous layers; merely summing
per-layer lower bounds is invalid.

\paragraph{Classical combinatorial exploration.}
Classical combinatorial pure exploration and Best-Set have mature
instance-dependent theory~\cite{chen2014cpe,chen2017nearly}, including matroid
best-basis identification~\cite{chen2016matroid}.  Any quantum comparison must
use the strongest same-interface classical method rather than uniform sampling.

\paragraph{Narrow candidate novelty.}
The only core claim retained for investigation is:
\begin{quote}
A constructive, fixed-confidence, heterogeneous-\emph{angular}-gap Top-$k$
algorithm, together with a matching lower bound, that is asymptotically stronger
on an explicit family than the best composition of approximate $k$-minimum,
quantum mean/amplitude estimation, variable-time search, multiple-marked
extraction, and quantum BAI.
\end{quote}
If that strict comparison cannot be proved, Q-GapSelect is an integration study,
not a new quantum algorithm.

\section{Two Oracle Layers}

\subsection{Layer C: canonical block rotation}

Let $\theta_i=\arcsin\sqrt{\mu_i}\in[0,\pi/2]$.  The canonical oracle is the
fully specified block rotation
\begin{equation}
 B_\mu=\sum_{i=1}^{n}\ket{i}\bra{i}\otimes R_y(2\theta_i),
 \qquad
 R_y(2\theta)=
 \begin{pmatrix}
 \cos\theta&-\sin\theta\\
 \sin\theta& \cos\theta
 \end{pmatrix}.
 \label{eq:block}
\end{equation}
Its action on both reward basis states is
\begin{align}
 B_\mu\ket{i}\ket{0}
 &=\ket{i}\bigl(\sqrt{1-\mu_i}\ket{0}+\sqrt{\mu_i}\ket{1}\bigr),\\
 B_\mu\ket{i}\ket{1}
 &=\ket{i}\bigl(-\sqrt{\mu_i}\ket{0}+\sqrt{1-\mu_i}\ket{1}\bigr).
 \label{eq:blockbasis}
\end{align}
Equations~\eqref{eq:block}--\eqref{eq:blockbasis} define the unitary on arbitrary
inputs by linearity and remove the phase/extension ambiguity in a one-column
oracle definition.  The model provides $B_\mu$, $B_\mu^\dagger$, and explicitly
requested controlled calls; each is counted.

Layer C is used for analytic experiments and as a clean hard subfamily for lower
bounds.  It is not assumed to be the free output of a reversible LLM generator.

\subsection{Layer P: natural purification sampler}

The broader interface prepares
\begin{equation}
 A\ket{i}\ket{0_W}\ket{0_R}
 =\ket{i}\left(
 \sqrt{1-\mu_i}\ket{\phi_{i,0}}\ket{0}
 +\sqrt{\mu_i}\ket{\phi_{i,1}}\ket{1}
 \right),
 \label{eq:purification}
\end{equation}
where normalized work states may depend on the arm and outcome.  A reversible
classical generator has the natural form requested by applications:
\begin{equation}
 A\ket{i}\ket{0_W}\ket{0_R}
 =\ket{i}\sum_w\sqrt{P_i(w)}\ket{w}\ket{R_i(w)},
 \qquad
 \mu_i=\Pr_{w\sim P_i}[R_i(w)=1].
 \label{eq:naturalsampler}
\end{equation}
The good projector and its reflection are
\begin{equation}
 \Pi_{\mathrm g}=I_I\otimes I_W\otimes\ket{1}\bra{1},
 \qquad S_{\mathrm g}=I-2\Pi_{\mathrm g}.
\end{equation}
The default access is $A$, $A^\dagger$, and the known good reflection.  Controlled
access is not silently assumed; a subroutine that needs it must state and charge
it.

The canonical block is a no-work special case of state preparation, but a general
sampler in~\eqref{eq:naturalsampler} cannot be replaced by $B_\mu$ at unit cost.
Doing so would erase $\ket{w}$ and synthesize a clean rotation whose angle is the
unknown success probability---essentially solving an estimation/transduction
problem.  Standard amplitude-estimation constructions can often work directly
with $A,A^\dagger,\Pi_{\mathrm g}$, but every Q-GapSelect subroutine and its error
composition must be re-proved in that access model.

\begin{obligation}[Purification transport]
Implement boundary tests, angular gap flags, batch extraction, filtering, and
certificate verification using only the declared Layer-P operations.  Prove the
claimed complexity without a free clean-rotation conversion, and account for
work-register size, uncomputation, state preparation, and controlled operations.
\end{obligation}

\subsection{What the lower bound can say}

For a fixed mean vector, different purifications can reveal different auxiliary
information through their work states.  A lower bound for $B_\mu$ is therefore a
lower bound for a canonical compatible sampler and, because canonical instances
belong to the broad state-preparation class, a \emph{worst-case compatible-sampler}
lower bound.  It is not an instance-wise lower bound for every $A$ with the same
success probabilities.  An all-purification statement would require a
no-leakage promise or a lower bound parameterized by full-state fidelity, neither
of which is currently proved.

\section{Top-k and Angular Gaps}

Assume $\mu_{(1)}\ge\cdots\ge\mu_{(n)}$ and the strict-boundary promise
$\mu_{(k)}>\mu_{(k+1)}$.  The fixed-confidence task returns
\[
S^\star=\TopK_k(\mu)
\quad\text{with probability at least }1-\delta.
\]
Because $\arcsin\sqrt{x}$ is increasing, let
$\theta_{(1)}\ge\cdots\ge\theta_{(n)}$ denote the correspondingly ordered angles.
Define the primary boundary gaps
\begin{equation}
\gamma_i=
\begin{cases}
\theta_i-\theta_{(k+1)},& i\in S^\star,\\
\theta_{(k)}-\theta_i,& i\notin S^\star.
\end{cases}
\label{eq:angulargap}
\end{equation}
The local coherent discrimination scale is
\begin{equation}
c_i=\Theta(1/\gamma_i),
\label{eq:localcost}
\end{equation}
since canonical reward states at angles $\theta$ and $\theta'$ have overlap
$\cos(\theta-\theta')$.  This is the cost supplied to any weighted-adversary or
variable-time composition.

For reporting and classical comparison we also retain the mean gaps
\begin{equation}
\Delta_i=
\begin{cases}
\mu_i-\mu_{(k+1)},& i\in S^\star,\\
\mu_{(k)}-\mu_i,& i\notin S^\star.
\end{cases}
\end{equation}
They are not interchangeable near $0$ or $1$.  If the compared means lie in
$[\eta,1-\eta]$, the mean-value theorem gives the interior relation
\begin{equation}
2\sqrt{\eta(1-\eta)}\,\gamma_i
\le \Delta_i\le\gamma_i.
\label{eq:interior}
\end{equation}
Thus a mean-gap corollary is permitted only with an explicit interior promise.

\section{Adaptive Certificate Orientation}

\subsection{Why fixed smaller-side orientation is rejected}

The Top-$k$ answer has two exact representations:
\[
S_+^\star=S^\star,\qquad S_-^\star=[n]\setminus S^\star.
\]
The earlier draft always enumerated whichever representation had smaller
cardinality.  This is false as an instance-sensitive rule.  Let $n=3m$, $k=m$,
place all $m$ selected arms at angular gap $\gamma$, one rejected arm at angular
gap $\gamma$, and the remaining $2m-1$ rejected arms at constant gap.  At the
fine scale, the selected orientation must extract $m$ hard outputs whereas the
rejected orientation extracts one.  The respective fine terms differ by
$\Theta(\sqrt m)$, although the selected set is smaller.  Choosing $\gamma$
sufficiently small makes that ratio dominate coarse work.  The rejected formula
and counterexample are preserved in
\texttt{docs/rejected\_candidates.md}.

\subsection{New orientation-aware candidate}

Set $\eps_r=(\pi/2)2^{-r}$ and
\begin{equation}
\ell_i=\min\{r\ge0:\eps_r\le\gamma_i\},\qquad
N_r=|\{i:\ell_i\ge r\}|.
\end{equation}
For $b\in\{+,-\}$ define
\begin{equation}
M_{r,b}=|S_b^\star\cap\{i:\ell_i=r\}|,
\end{equation}
\begin{equation}
\mathcal H_b(\theta,k)
=\sum_{r=0}^{\max_i\ell_i}
\frac{\sqrt{N_r(M_{r,b}+1)}}{\eps_r},
\qquad
\mathcal H_{\mathrm{orient}}
=\min\{\mathcal H_+,\mathcal H_-\}.
\label{eq:horient}
\end{equation}
Equation~\eqref{eq:horient} is a candidate accounting functional, not a theorem.
The $+1$ charges a certification stage even when no output item is first resolved
at that scale.

The algorithm does not know in advance which orientation minimizes
\eqref{eq:horient}.  The proposed remedy is to dovetail two resumable procedures:
one certifies a size-$k$ selected set; the other certifies a size-$(n-k)$ rejected
set whose complement is returned.  Query budgets double geometrically and are
interleaved.  A candidate is accepted only after an independent cross-boundary
certificate verifier succeeds.  The first verified certificate wins.  A
constant-overhead first-finish bound for random, variable-time quantum
subroutines is itself a proof obligation.

\begin{obligation}[Orientation dovetail]
Define resumable selected/rejected procedures, failure budgets, and certificate
verification.  Prove that the first valid certificate is correct and that the
total cost is within a constant/polylogarithmic factor of the faster valid
orientation, without assuming its identity.
\end{obligation}

\section{Proposed Q-GapSelect Architecture}

For orientation $b$, the proposed staged procedure is:
\begin{enumerate}[leftmargin=*,label=\textbf{Step \arabic*.}]
  \item At angular scale $\eps_r$, obtain a coarse order-statistic boundary using
  an approximate $k$-minimum/order-statistic routine.  This is a known component
  ~\cite{gao2025approxkmin,nayak1999median}.
  \item Construct a reversible three-way angular classifier: certified in,
  certified out, or unresolved.  Compose arm-dependent stopping costs with a
  variable-time routine; variable-time search itself is known
  ~\cite{ambainis2023variable}.
  \item Enumerate newly certified elements of $S_b^\star$ using a multiple-marked
  routine~\cite{vanapeldoorn2024marked}.  Independently verify measured outputs.
  \item Maintain an explicitly charged reversible activity predicate.  No rejected
  list, QROM table, or previous confidence computation is free.
  \item Allocate $\delta_r=6\delta/(\pi^2(r+1)^2)$, emit a candidate certificate
  when the orientation quota is reached, and submit it to the independent
  verifier.
\end{enumerate}
The main Q-GapSelect controller dovetails $b=+$ and $b=-$ and returns the first
verified representation.

\begin{conjecture}[Canonical heterogeneous-gap upper candidate]
Under Layer-C access, a constructive Q-GapSelect algorithm returns the exact
Top-$k$ set with probability at least $1-\delta$ using
\begin{equation}
\widetilde O\!\left(
\mathcal H_{\mathrm{orient}}(\theta,k)
\polylog(n,1/\delta,1/\gamma_{\min})
\right)
\label{eq:canonicalupper}
\end{equation}
canonical oracle calls and polynomial auxiliary time.
\end{conjecture}

\begin{conjecture}[Natural-sampler transport candidate]
Under Layer-P access, the same asymptotic reward-query expression is achievable
using $A,A^\dagger,\Pi_{\mathrm g}$, plus explicitly reported generator and
reversible-checker resources.
\end{conjecture}

Neither conjecture is implied by listing the known subroutines.  The required
advance is their fixed-confidence heterogeneous composition with certified output
and no worst-gap multiplication.

\begin{obligation}[Strict black-box separation]
Derive the strongest upper bound obtained by composing
Gao--Ji--Wang approximate $k$-minimum, quantum mean/amplitude estimation,
Ambainis--Kokainis--Vihrovs variable-time search,
van Apeldoorn--Gribling--Nieuwboer extraction, Wang et al.\ quantum BAI, and
Wang--Xu--Zhang $k$-minimum data structures.  Exhibit an explicit heterogeneous
profile on which~\eqref{eq:canonicalupper} is asymptotically smaller.  Without this
separation the novelty claim is rejected.
\end{obligation}

\begin{obligation}[Boundary and noisy predicate composition]
Prove adaptive correctness and cost when an approximate boundary is reused inside
a bounded-error, variable-time marking predicate.  Existing approximate
$k$-minimum and bounded-error search are baselines, not proof shortcuts.
\end{obligation}

\begin{obligation}[Implicit filtering and verification]
Implement reversible filters and a cross-boundary certificate verifier with all
work qubits uncomputed.  Bound repeated history access, QROM, arithmetic, and
verification rather than hiding them behind one oracle call.
\end{obligation}

\section{Lower-Bound Program}

For canonical hard instances, encode hypotheses as angular pairs around an
interior angle $\theta_0$, for example
$\theta_i\in\{\theta_0-\gamma_i,\theta_0+\gamma_i\}$.  Single-coordinate
distinguishability costs $\Omega(1/\gamma_i)$.  Equal-gap fixed-weight recovery is
a required sanity reduction, but is not proposed as new because approximate
$k$-minimum, marked extraction, and order-statistic results already cover its
core phenomena~\cite{gao2025approxkmin,vanapeldoorn2024marked,nayak1999median}.

The potential new lower bound requires disjoint dyadic angular-gap blocks and
orientation-aware output multiplicities.  The relevant exploratory cost vector
is $c_i=\Theta(1/\gamma_i)$ in a weighted adversary quantity
$\Adv_{\TopK}(c)$~\cite{lee2011stateconversion,reichardt2011reflections}.  We do
not claim that it equals $\mathcal H_{\mathrm{orient}}$.

\begin{obligation}[Dyadic direct sum]
Construct a promised canonical family for which solving Top-$k$ recovers every
designated block.  Use adversary composition or a strong direct-product theorem
to control superposition queries across blocks; adding separate lower bounds is
not valid.
\end{obligation}

\begin{obligation}[Orientation-aware lower target]
Prove a lower bound matching the minimum over valid selected/rejected
representations, or replace~\eqref{eq:horient} with a rigorously derived relation
complexity.  The lower bound must hold against all adaptive quantum algorithms,
not only estimate-then-sort methods.
\end{obligation}

\begin{obligation}[Compatible-sampler scope]
State the result as a canonical lower bound and hence a worst-case lower bound
over compatible purification samplers.  Do not transfer it to every purification
with the same mean vector unless a no-leakage theorem is proved.
\end{obligation}

\begin{obligation}[Same-interface classical comparison]
Give the strongest classical upper and lower bounds using basis-state samples
from the same generator.  Confidence, output relation, preprocessing, and oracle
construction must match the quantum comparison.
\end{obligation}

\section{Deferred Matroid Extension}

Let $\cM=(E,\mathcal I)$ be a rank-$r$ matroid with unique maximum-mean basis
\[
B^\star=\arg\max_{B\in\cB(\cM)}\sum_{e\in B}\mu_e.
\]
Classical best-basis identification is established~\cite{chen2016matroid}.
Because $\theta=\arcsin\sqrt{\mu}$ preserves order, exchange comparisons can be
measured by angular gaps.  If $C_{B^\star}(f)$ is the fundamental circuit of
$f\notin B^\star$, candidate exchange gaps are
\[
\gamma_f=\min_{e\in C_{B^\star}(f)\setminus\{f\}}(\theta_e-\theta_f),
\]
and, for $e\in B^\star$,
\[
\gamma_e=\theta_e-
\max\{\theta_f:f\notin B^\star,\ e\in C_{B^\star}(f)\}.
\]
If the displayed exchange set is empty, define $\gamma_e=+\infty$; such an
element has no outside exchange competitor and contributes no finite local
exchange-discrimination cost.

Q-BatchExchange would search uncertain exchanges, batch-certify basis-in/out
elements, and contract/delete them.  It may dovetail a primal-basis certificate
and a dual-cobasis certificate, but reversible dual-independence access must be
charged.  This is a \status{proposed extension}, not a result.

\begin{obligation}[Constructive matroid algorithm]
Avoid enumerating bases or all exchange pairs.  Bound reward and reversible
independence-oracle queries, auxiliary time, memory, and state preparation.
Recover the audited uniform-matroid theorem as a special case.
\end{obligation}

\begin{obligation}[Partition direct sum]
For independent partition groups, prove the necessary direct-sum behavior.  A
global square root across required independent outputs is a rejection condition.
\end{obligation}

\section{Experimental Falsification Plan}

The current implementation has two analytic Layer-C pipelines.  One evaluates
deterministic complexity proxies; the other independently estimates every
active arm while sampling analytic Grover measurement laws.  Their executed
query ledgers and candidate-theory accounting are separate.  Neither implements
\textsc{QBoundary}, coherent batch extraction, orientation dovetail, or Layer-P
transport; passing its tests activates no asymptotic claim.

\paragraph{Current artifact and pre-registered expansion.}
The implemented \texttt{run\_scaling} pipeline evaluates five deterministic
mean-space equal/geometric analytic-proxy regimes; its \texttt{trials} field is
not used to repeat calculations.  Separately, \texttt{run\_reference} executes
four fixed mean-vector instances over a configurable number of derived random
seeds.  It uses \texttt{trials} as its loop count and randomly samples the
analytic measurement law of each requested Grover experiment.  This is a
multi-seed analytic-measurement regression, not a coherent index-register batch
circuit and not random instance generation.  The checked-in reference artifact
is a four-trial-per-scenario diagnostic (16 records), whereas the configuration's
500-trial default has no committed run artifact.  Both pipelines are code sanity
checks only and are not evidence for the candidate theorem.  Each reference
record and aggregate separates \texttt{certified\_exact\_recovery}, which requires
interval resolution and exact output, from
\texttt{heuristic\_inclusive\_exact\_recovery}, which also counts exact outputs
produced by empirical completion after a timeout.  Only the former is eligible
as an empirical fixed-confidence success; the latter is a diagnostic and cannot
be used to mask unresolved trials.

The future experimental campaign will generate instances in angle space and map
them by $\mu_i=\sin^2\theta_i$.  Before running that campaign, we will
pre-register
\[
n\in\{8,16,32,64,128,256\},\quad
k\in\{1,2,4,\lfloor n/4\rfloor,\lfloor n/2\rfloor\},\quad
\delta\in\{0.05,0.01\}.
\]
The pre-registered future random-instance families will include equal angular
gaps, geometric angular gaps, clustered boundaries, planted dyadic blocks,
endpoint regimes, and the complement-asymmetry counterexample.  Both $\gamma_i$
and $\Delta_i$ will be stored.  At least 500 independently generated instances
will be used per random-instance configuration.  This proposed instance count
is distinct from the already implemented multi-seed measurement repetition of
four fixed instances and has not been executed.

\paragraph{Required quantum baselines.}
We compare against: uniform amplitude estimation plus sorting; adaptive per-arm
mean estimation; approximate $k$-minimum with charged expectation-value oracle
~\cite{gao2025approxkmin}; variable-time search over arm-specific classifiers
~\cite{ambainis2023variable}; multiple-marked extraction at each layer
~\cite{vanapeldoorn2024marked}; quantum BAI in its valid single-output regime
~\cite{wang2021quantum}; and a time-efficient $k$-minimum implementation where
its input model applies~\cite{wang2026rmq}.  Classical baselines include the
strongest implemented fixed-confidence Top-$k$/Best-Set allocation, not only
uniform sampling.

\paragraph{Oracle audit.}
Layer-C and Layer-P experiments are separate.  Layer-P manifests record work
registers, $A/A^\dagger$ calls, good reflections, controlled calls, and generator
cost.  No experiment replaces Layer P by a clean $R_y$ without recording the
conversion algorithm and its cost.

\paragraph{Reporting.}
Primary synthetic outcomes are certified exact-set recovery, interval-resolution
and timeout rates, forward/inverse/controlled queries, verifier calls, failure
type, simple regret, and peak coherent resources.  Heuristic-inclusive exact
recovery is reported separately and never treated as fixed-confidence success.
Simulator wall time, gates, depth, qubits, CPU/GPU time, and memory are separate.
Finite scaling slopes are empirical diagnostics, never proofs of a polynomial
separation.

\section{Mapping to Attacks on Code LLMs}

Black-box attacks already steer code models toward insecure completions
~\cite{hajipour2023codelmsec,jenko2025insec}, and semantics-preserving
cross-origin context poisoning is a strong baseline~\cite{storek2026xoxo}.  Our
exact application mapping is attack-\emph{portfolio} selection rather than an
unvalidated additive composition of atomic edits.

For complete semantics-preserving variant $e$, task/seed randomness $w=(t,z)$,
source generator $M$, full functional oracle $F$, and exploit-confirmed oracle
$V$, define
\[
R_e(w)=\mathbf1\{F(M(T_e(p_t),z))=1\land
                  V(M(T_e(p_t),z))=1\},
\qquad \mu_e=\mathbb E_wR_e(w).
\]
A reversible open-source implementation naturally prepares
\begin{equation}
A_{\mathrm{LLM}}\ket{e}\ket{0}
=\ket{e}\sum_w\sqrt{P_e(w)}
 \ket{w,M(T_e(p_t),z),F,V}\ket{R_e(w)}.
\label{eq:llmsampler}
\end{equation}
This is Layer P, with large generator/checker garbage; it is not a clean
single-qubit $R_y$.  Building and reversing~\eqref{eq:llmsampler}, including
token generation, tests, exploit checkers, finite precision, and storage, must be
charged.  After measurement, selected prompts are sent classically to held-out
victims.  Proprietary APIs are never coherent oracles.

Until the purification-transport theorem and a credible reversible resource
analysis are complete, the LLM study cannot claim a genuine quantum-query
advantage.  It may report a classical simulation of a selector or a source-side
oracle study under those exact labels.

\paragraph{Endpoints.}
For a pre-registered attack predicate $G$ and victim budget $Q$,
\begin{align}
\mathrm{ASR@Q}
&=\frac1{|\cT|}\sum_{t\in\cT}
\mathbf1\{\exists q\le Q:G(c_{tq})=1\},\\
\mathrm{FV\mbox{-}ASR@Q}
&=\frac1{|\cT|}\sum_{t\in\cT}
\mathbf1\{\exists q\le Q:F(c_{tq})=1\land V(c_{tq})=1\},\\
\Delta\mathrm{\mbox{-}FV\mbox{-}ASR@Q}
&=\mathrm{FV\mbox{-}ASR@Q}_{\mathrm{attack}}
-\mathrm{FV\mbox{-}ASR@Q}_{\mathrm{clean}}.
\end{align}
The primary $Q$ is frozen before test access.  We also report functionality
retention, fresh-seed success, timeouts/indeterminate outcomes, source-to-victim
transfer, query-to-first-success, and separate budgets for quantum/source/victim/
checker calls.

CWEval, BaxBench, and SecRepoBench provide functionality/security or
repository-level evaluation~\cite{peng2025cweval,vero2025baxbench,shen2026secrepobench}.
Splits are by task, repository, CWE, and model family.  Repeated generations of
one task never cross splits.  Victim outputs remain sealed until variants,
selector, baselines, and endpoint are frozen.

\section{Ethical and Claim Boundaries}

Generated code and exploits execute only in authorized, network-isolated
benchmark containers.  No third-party systems, accounts, or infrastructure are
targeted.  Novel vulnerabilities are privately disclosed; operational payloads
are redacted when publication would materially enable abuse.  The study does not
automate deployment, persistence, credential theft, or lateral movement.

A new-quantum-algorithm claim activates only after:
\begin{enumerate}[leftmargin=*]
  \item the Layer-C heterogeneous upper bound is complete and constructive;
  \item it strictly beats the strongest black-box composition on an explicit
  family;
  \item an all-adaptive-algorithms canonical lower bound matches it, with honest
  worst-case sampler scope;
  \item orientation dovetail, verification, state preparation, QROM, and
  reversible filters are polynomial and charged;
  \item if an LLM quantum advantage is claimed, Layer-P transport and reversible
  generator resources are also complete.
\end{enumerate}
Equal-gap recovery, QBoundary, batch extraction, simulator speed, or favorable
unrun tables activate none of these claims.

\section{Conclusion}

After oracle, gap, orientation, and literature audit, Q-GapSelect is a narrower
and higher-risk research candidate than the original draft.  Its only plausible
algorithmic novelty is a tight heterogeneous-angular-gap, fixed-confidence
multi-output theorem that survives comparison with approximate $k$-minimum,
variable-time search, marked extraction, order statistics, and quantum BAI.  The
canonical theorem, natural-sampler transport, direct-sum lower bound, matroid
extension, and LLM attack effect all remain open.  The correct next step is to
prove or falsify those obligations; no quantum advantage is presently claimed.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
